Morphological diversity in tenrecs (Afrosoricida, Tenrecidae): Comparing tenrec skull diversity to their closest relatives

### 2015-01-28 paper/Diversity_MS.tex
Edits to intorduction and preamble

% Preamble
\documentclass[12pt,a4paper]{article}
\usepackage{enumerate} 	% put in numbers or bullet points
\usepackage{setspace}	% line spacing					
\usepackage{authblk}	% For author affiliations
\usepackage{graphicx} 	% For adding pictures

\usepackage[nomarkers]{endfloat} %Figures and tables at the end of the document
\usepackage{pdflscape}	% for landscape pages
\usepackage{mathtools}	% For equations etc.
\usepackage[osf]{mathpazo} % palatino font package
\usepackage{fixltx2e}	% includes subscripts
\usepackage{ms}     	% load the manuscript style template - may need to change this for PeerJ
\usepackage{hyperref} %need this for url references

\setcounter{secnumdepth}{0} % removes numbers from section headings
\raggedright 			% justify the text on the left only
\pagenumbering{arabic}	% Page numbers

\usepackage[round]{natbib} % author-year citations in round brackets

%-----------------------------------------
%Current title page 
%NB PeerJ don't want a title page: just the author details but I haven't figured out how to do that without losing the formatting of the rest of the manuscript
%I may need to get rid of the lists of tables and figures at the end: they want titles and legends to be on the same page as the figure/table
%----------------------------------------

%---------------------------------------------------------------
% Start of document
\begin{document}
\modulolinenumbers[1] 	% Line numbering on every line

\parindent=1.5em		% Changes paragraph indenting so it's not so big
\addtolength{\parskip}{.3em} % Changes spacing between sections so it's smaller

\noindent
\textsc{Sive Finlay$^{1,2}$ and Natalie Cooper$^{1,2,*}$}\\

@@

\newpage
%****************************************************
%Abstract
%Peer J wants the abstract as a separate document

%This is the abstract from my thesis

	%Patterns of morphological diversity (the variety of physical form) have important implications for our understanding of species ecology and evolution. Some clades such as cichlid fish and anole lizards are known for their high morphological diversity. Studying these groups can provide insights into the processes that led to the evolution of this exceptional diversity. 
	%Morphological diversity is often studied qualitatively. However, to truly understand the evolution of diversity, it is important to take a quantitative approach instead of relying on subjective, qualitative assessments. Here, we present a quantitative analysis of morphological diversity in a Family of small mammals, the tenrecs (Afrosoricida, Tenrecidae). 
	%Tenrecs are often cited as an example of an exceptionally morphologically diverse group. However, this assumption has not been tested quantitatively. We use geometric morphometric analyses of skull shape to test whether tenrecs are more morphologically diverse than their closest relatives, the golden moles (Afrosoricida, Chrysochloridae). Tenrecs occupy a wider range of ecological niches than golden moles so we predicted that they would be more morphologically diverse. 
	%Contrary to our expectations, We found that tenrec skulls are only more morphologically diverse than golden moles when measured in lateral view. Furthermore, similarities among the species-rich \textit{Microgale} tenrec Genus appear to mask higher morphological diversity in the rest of the Family. These results reveal new insights into the morphological diversity of tenrecs and highlight the importance of using quantitative methods to test qualitative assumptions about patterns of morphological diversity.

%****************************************************
\section{Introduction}

	Analysing patterns of morphological diversity has important implications for our understanding of ecological and evolutionary traits. For example, from a functional ecology perspective, morphological characteristics of limbs inform us about locomotory style \citep[e.g.][]{Bou1987} and the trophic niches associated with particular dental morphologies affect speciation and diversification rates through time \citep{Price2012}. Morphological diversity is also an important aspect of evolutionary patterns such as adaptive radiations and convergent evolution. High morphological diversity is a unifying \citep{Losos2010a, Olson2009}, although not defining \citep{Glor2010, Olson2009}, characteristic of adaptive radiations. Furthermore, analysing morphological convergences in groups such as freshwater cichlid fish \citep{Muschick2012} and anole lizards \citep{Mahler2013} gives interesting insights into the relative repeatability of evolution \citep{Losos2011}.

	Although studies of morphological diversity have clear implications for our understanding of ecological and evolutionary patterns, apart from a few examples \citep[e.g.][]{Ruta2013, Goswami2011, Brusatte2008}, it is still common to study morphological diversity from a qualitative rather than quantitative perspective. However, we need to quantify the morphological similarities and differences among species to gain a better understanding of their ecological interactions and evolutionary history. Unfortunately, morphological diversity is difficult to quantify. Studies are inevitably constrained to measure the diversity of specific traits rather than overall morphologies \citep{Roy1997}. In addition, our perception of morphological diversity is influenced by the trait being used. One study of pterosaurs demonstrated that comparing the diversity of different morphological traits using varying methods produced similar results \citep{Foth2012}. However, it remains unclear whether this finding can be applied to all vertebrate groups: in some species, comparing the relative diversity of cranial and limb morphologies may yield different results \citep{Foth2012}. Furthermore, linear measurements of morphological traits can restrict our understanding of overall morphological variation. A distance matrix of measurements between specific points is unlikely to give a completely accurate representation of a three dimensional structure \citep{Rohlf1993}.

	These are important limitations to consider but geometric morphometric approaches help to overcome some of the issues associated with traditional morphological studies \citep{Adams2004}. Morphometric studies based on caliper measurements of particular features can only describe a limited set of distances, ratios and angles which often fail to capture the overall shape of a specific structure \citep{Slice2007}. Geometric morphometrics circumvents these issues by using a system of Cartesian landmark coordinates to define anatomical points. This method captures more of the true, overall anatomical shape of particular structures \citep{Mitteroecker2009}. These more detailed approaches are useful tools for studying patterns of morphological diversity.

	Here we apply geometric morphometric techniques to quantify morphological diversity in a Family of small mammals, the tenrecs. Tenrecs (Afrosoricida, Tenrecidae) are a morphologically diverse group that is commonly cited as an example of both convergent evolution and an adaptive radiation \citep{Soarimalala2011, Eisenberg1969}. The Family is comprised of 34 species, 31 of which are endemic to Madagascar \citep{Olson2013}. Body masses of tenrecs span three orders of magnitude (2.5 to > 2,000g); a greater range than all other Families, and most Orders, of living mammals \citep{Olson2003}. Within this vast size range there are tenrecs which convergently resemble shrews (\textit{Microgale} tenrecs), moles (\textit{Oryzorictes} tenrecs) and hedgehogs \citep[\textit{Echinops} and \textit{Setifer} tenrecs,][]{Eisenberg1969}. Their similarities include examples of morphological, behavioural and ecological convergence \citep{Soarimalala2011}. Tenrecs are one of only four endemic mammalian clades in Madagascar and the small mammal species they resemble are absent from the island \citep{Garbutt1999}. Therefore, it appears that tenrecs represent an adaptive radiation of species which filled otherwise vacant ecological niches \citep{Soarimalala2011}.
	The similarities among tenrecs and other small mammals are even more remarkable when you consider their phylogenetic history. Tenrecs were originally classified within the general "Insectivora" clade and only molecular studies revealed their true phylogenetic affinities within the Afrotherian mammals \citep{Stanhope1998}. Therefore, despite initial appearances, tenrecs are more closely related to elephants, manatees and aardvarks than they are to shrews, moles or hedgehogs.

	Although tenrecs are often cited as an example of both an adaptive radiation and exceptional convergent evolution, these claims have not been investigated quantitatively. There are qualitative similarities among the hind limb morphologies of tenrecs and several other unrelated species with similar locomotory styles \citep{Salton2009} but the degree of morphological similarity has not been established. Morphological diversity is an important feature of adaptive radiations \citep{Losos2010a} and it also informs our understanding of convergent phenotypes \citep{Muschick2012}. Therefore, it is important to quantify patterns of morphological diversity in tenrecs to gain an insight into their evolution.

@@

	%Might need more to finish off the introduction?
%************************************
\section{Materials and Methods}

	The methods we used involved several steps of i) data collection, ii) geometric morphometric analyses and iii) estimating morphological diversity. For clarity,  Figure \ref{fig:flow} summarises all of these steps and we describe them in detail below.

%Methods flow chart
	\begin{figure}[!htbp]
	\centering
	\includegraphics[width=1\linewidth,height=0.8\textheight]{figures/methods_flowchart_paper.png}

@@

\subsection{Data collection}
	One of us (SF) used the collections of five museums: the Natural History Museum, London (BMNH), the Smithsonian Institute Natural History Museum, Washington D.C. (SI), the American Museum of Natural History, New York (AMNH), the Museum of Comparative Zoology, Cambridge M.A. (MCZ) and the Field Museum of Natural History, Chicago (FMNH). We recorded species names as they were written on museum specimen labels and then corrected them to match the taxonomy in Wilson and Reeder's Mammal Species of the World \citeyearpar{Wilson2005}. For recently identified species,  which are not included in Wilson and Reeder \citeyearpar{Wilson2005}, we used the taxonomy recorded on the specimen labels. Wilson and Reeder \citeyearpar{Wilson2005} record 30 species of tenrec but more recent studies indicate that there are now 34 species \citep[][]{Olson2013}. The additional species belong to the shrew tenrec (\textit{Microgale}) Genus and represent either recognition of cryptic species boundaries \citep{Olson2004} or discovery of new species \citep{Goodman2006, Olson2009}. Only one of these four recent additions, \textit{M. jobihely}, was present in the museum collections and therefore we could not include the three other newly recognised species in the analyses. 
 	We photographed all of the tenrec and golden mole skulls available in the collections. This included 31 of the 34 species in the tenrec Family and 12 of the 21 species of golden moles \citep{Wilson2005}.
	%Left out the points about male/female and adult/juvenile

	We took pictures of the skulls using photographic copy stands consisting of a camera attachment with an adjustable height bar, a flat stage on which to place the specimen and an adjustable light source. To take possible light variability into account, on each day we took a photograph of a white sheet of paper and used the custom white balance function on the camera to set the image as the baseline "white" measurement for those particular light conditions.

	We photographed the specimens with a Canon EOS 650D camera fitted with a EF 100 mm f/2.8 Macro USM lens. We used a remote control (H\"ahnel Combi TF) to take the photos to avoid shaking the camera and distorting the images. We photographed the specimens on a black material background with a light source in the top left-hand corner of the photograph. We used small bean bags as necessary to hold the specimens in position while being photographed to ensure that they lay in a flat plane relative to the camera and did not tilt in any direction. We used the grid-line function on the live-view display screen of the camera to position the specimens in the centre of each image.

	We photographed the skulls in three views: dorsal (top of the cranium), ventral (underside of the skull with the palate roof facing upwards) and lateral (right side of the skull) (Figure \ref{fig:flow}). When the right sides of the skulls were damaged or incomplete we photographed the left sides and later reflected the images so that they could be compared to pictures of the right sides \citep[e.g.][]{Barrow2008}.

	We converted the raw files to binary (grey scale) images and re-saved them as TIFF files \citep[uncompressed files preserve greater detail, ][]{RHOI2013}. 
	Photographs of the specimens from the American Museum of Natural History and the Smithsonian Institute are available on figshare in separate file sets for the dorsal \citep{Finlay2013d}, ventral \citep{Finlay2013v} and lateral \citep{Finlay2013l} skull pictures. Copyright restrictions from the other museums prevent public sharing of their images but they are available on request.

@@

%Maybe move this to the supplementary?
	When using semilandmark approaches there is a potential problem of over - sampling: simpler structures will require fewer semilandmarks to accurately represent their shape  \citep{MacLeod2012}. To ensure that we applied a uniform standard of shape representation to each outline segment (i.e. that simple structures would not be over-represented and more complex features would not be under-represented), we followed the method outlined by MacLeod \citeyearpar{MacLeod2012}. For each data set we chose a random selection of photos of specimens which represented the breadth of the morphological data (i.e. specimens from each sub-group of species). We drew the appropriate curves on each specimen and over-sampled the number of points on the curves. We measured the length of the line and regarded that as the 100\%, true length of that outline. We then re-sampled the curves with decreasing numbers of points and measured the length of the outlines. We calculated the length of each re-sampled curve as a percentage of the total length of the curve and then found the average percentage length for that reduced number of semilandmark points across all of the specimens in my test file. We continued this process until we found the minimum number of points that gave a curve length which was at least 95\% accurate.  We repeated these curve-sampling tests for each analysis to determine the minimum number of semilandmark points which would give accurate representations of morphological shape.

@@

@@

	For each analysis, we used the gpagen function in the geomorph package \citep{Adams2013} to run a general Procrustes alignment \citep{Rohlf1993} of the landmark coordinates while sliding the semilandmarks by minimising Procrustes distance \citep{Bookstein1997}. We used these Procrustes-aligned coordinates of all specimens to calculate average shape values for each species which we then used for a principal components (PC) analysis with the plotTangentSpace function \citep{Adams2013}. We selected the number of principal component (PC) axes that accounted for 95\% of the variation in the data (Figure \ref{fig:flow}) and used these axes to estimate morphological diversity in each Family.
%-------------------------------------------------------	
\subsection{Estimating morphological diversity}

	We grouped the PC scores for tenrecs and golden moles separately so that we could estimate the diversity of each Family and then compare the two groups (Figure \ref{fig:flow}). We compared morphological diversity in two ways. First, we used non parametric multivariate analysis of variance \citep[npMANOVA;][]{Anderson2001} to test whether tenrecs and golden moles occupied significantly different positions within the morphospaces defined by the PC axes that accounted for 95\% of the overall variation in the data \citep[e.g.][]{Serb2011, Ruta2013}. A significant difference between the two Families would indicate that they have unique morphologies which do not overlap. Second, we compared morphological diversity within tenrecs to the diversity within golden moles. We define morphological diversity as the mean Euclidean distance (sum of squared differences) between each species and its Family centroid (Figure \ref{fig:centroids}). This is summarised in the equation below where \textit{n} is the number of species in the Family, \textit{i} is the number of PC axes and \textit{c} are the average PC scores for each axis (the centroid).

@@

	In addition to the differences among the three skull views, our results indicate that, in skulls at least, the overall morphological diversity within tenrecs is not as large as is often assumed \citep[e.g.][]{Eisenberg1969, Olson2013}. Studies of morphological variation are sensitive to the sampling used. If a particular morphotype is over-represented then the similarities among those species will reduce the overall morphological variation within the group \citep{Foote1991}. This appears to be the case for our data; it was only when we included a sub-sample of \textit{Microgale} tenrecs that we found higher morphological diversity in tenrecs compared to golden moles across all three skull analyses (Table \ref{tab:diversity}).
	While there are clear physical differences among Family members \citep{Olson2013, Eisenberg1969}, the majority of tenrecs are very morphologically similar \citep{Jenkins2003} so morphological diversity in the Family as a whole is not as large as it first appears.  
	The goal of our study was to quantify morphological variation in tenrecs instead of relying on subjective assessments of their high morphological diversity \citep{Olson2013, Soarimalala2011, Eisenberg1969}. However, it is difficult to quantify overall morphological diversity because any study is inevitably constrained by its choice of specific traits \citep{Roy1997}. Variation in skull shape is only one aspect of overall morphology. Quantifying variation in other morphological traits could yield different patterns. Therefore future work should extend our approach beyond skulls to gain a more complete understanding of the overall morphological diversity of tenrecs and golden moles.
	%I combined the paragraph above within the discussion (previously it was part of a separate caveats section)
	While recognising these limitations, our results provide valuable insights into the differences between subjective and quantitative assessments of morphological diversity. 
%**********************************
\section{Conclusions}
	We have presented the first quantitative investigation of morphological diversity in tenrecs. Our results indicate that, overall, tenrec skulls are not more morphologically diverse than golden moles and that similarities among the species rich \textit{Microgale} tenrecs mask signals of higher morphological diversity among the rest of the Family. Of course the results presented here are restricted to just one axis of morphological variation and further analysis of other traits is required. However, our findings provide a foundation for future investigations and represent a significant step towards a more quantitative understanding of patterns of morphological and evolutionary diversity in tenrecs. 
%*******************************
\section{Acknowledgements} %PeerJ have a separate section for funding acknowledgements
	We thank Thomas Guillerme, Fran\c{c}ois Gould and the members of NERD club for their insightful discussions and comments. Thank you to museum staff and curators for facilitating our access to their collections: Leona Leonard and Nigel Monaghan (Natural History Museum, Ireland), Roberto Portela Miguez and Paula Jenkins (Natural History Museum, London), Esther Langan (Smithsonian Institute NMNH), Eileen Westwig (American Museum of Natural History), Judy Chupasko (Museum of Comparative Zoology) and Bill Stanley and Steve Goodman (Field Museum).
%********************************
\bibliographystyle{sysbio} 
\bibliography{refs_paper}

>>>>

% Preamble
\documentclass[12pt,a4paper]{article}
\usepackage{enumerate} 	
\usepackage{setspace}						
\usepackage{authblk}	
\usepackage{graphicx} 	
\usepackage[nomarkers, nolists]{endfloat} 
\usepackage{pdflscape}	
\usepackage{mathtools}	
\usepackage[osf]{mathpazo} 
\usepackage{fixltx2e}	
\usepackage{lineno}    	
\usepackage{hyperref}
\usepackage[round]{natbib} 
\usepackage{setspace}

\setcounter{secnumdepth}{0} 
\raggedright 			
\pagenumbering{arabic}	
\linenumbers

% Start of document
\begin{document}

\parindent=1.5em		
\addtolength{\parskip}{.3em} 
\doublespace

% Title page
\noindent
\textsc{Sive Finlay$^{1,2}$ and Natalie Cooper$^{1,2,*}$}\\

@@

% Abstract

	% Morphological diversity is often studied qualitatively. However, to truly understand the evolution of exceptional diversity, it is important to take a quantitative approach instead of relying on subjective, qualitative assessments. Here, we present a quantitative analysis of morphological diversity in a Family of small mammals, the tenrecs (Afrosoricida, Tenrecidae).

	% Tenrecs are often cited as an example of an exceptionally morphologically diverse group. However, this assumption has not been tested quantitatively. We use geometric morphometric analyses of skull shape to test whether tenrecs are more morphologically diverse than their closest relatives, the golden moles (Afrosoricida, Chrysochloridae). Tenrecs occupy a wider range of ecological niches than golden moles so we predict that they will be more morphologically diverse.

	% Contrary to our expectations, We find that tenrec skulls are only more morphologically diverse than golden moles when measured in lateral view. Furthermore, similarities among the species-rich \textit{Microgale} tenrec Genus appear to mask higher morphological diversity in the rest of the Family. These results reveal new insights into the morphological diversity of tenrecs and highlight the importance of using quantitative methods to test qualitative assumptions about patterns of morphological diversity.

\newpage
\section{Introduction}

	Analysing patterns of morphological diversity has important implications for our understanding of ecological and evolutionary traits. Species morphology can influence niche occupancy and affect speciation and diversification rates through time \citep{Price2012}. High morphological diversity is also a unifying \citep{Losos2010a, Olson2009}, although not defining \citep{Glor2010, Olson2009}, characteristic of adaptive radiations. Furthermore, analysing morphological convergences in groups such as freshwater cichlid fish \citep{Muschick2012} and anole lizards \citep{Mahler2013} provides insights into the relative repeatability of evolution \citep{Losos2011}.

	Although studies of morphological diversity have clear implications for our understanding of ecological and evolutionary patterns, apart from a few examples \citep[e.g.][]{Ruta2013, Goswami2011, Brusatte2008}, it is still common to study morphological diversity from a qualitative rather than quantitative perspective. However, we need to quantify the morphological similarities and differences among species to gain a better understanding of their ecological interactions and evolutionary history. Unfortunately, morphological diversity is difficult to quantify. Studies are inevitably constrained to measure the diversity of specific traits rather than overall morphologies \citep{Roy1997}. In addition, our perception of morphological diversity is influenced by the trait being used, and results may depend on the particular trait being analysed \citep{Foth2012}. Furthermore, linear measurements of morphological traits can restrict our understanding of overall morphological variation; a distance matrix of measurements among specific points is unlikely to give a completely accurate representation of a three dimensional structure \citep{Rohlf1993}. Geometric morphometric approaches can circumvent some of these issues by using a system of Cartesian landmark coordinates to define anatomical points \citep{Adams2004}. This method captures more of the true, overall anatomical shape of particular structures \citep{Mitteroecker2009}. These more detailed approaches are useful tools for studying patterns of morphological diversity.

	Here we apply geometric morphometric techniques to quantify morphological diversity in a Family of small mammals, the tenrecs. Tenrecs (Afrosoricida, Tenrecidae) are a morphologically diverse group that is commonly cited as an example of both convergent evolution and an adaptive radiation \citep{Soarimalala2011, Eisenberg1969}. The Family is comprised of 34 species, 31 of which are endemic to Madagascar \citep{Olson2013}. Body masses of tenrecs span three orders of magnitude (2.5 to $>$ 2,000g); a greater range than all other Families, and most Orders, of living mammals \citep{Olson2003}. Within this vast size range there are tenrecs which convergently resemble shrews (\textit{Microgale} tenrecs), moles (\textit{Oryzorictes} tenrecs) and hedgehogs \citep[\textit{Echinops} and \textit{Setifer} tenrecs,][]{Eisenberg1969}. Their similarities include examples of morphological, behavioural and ecological convergence \citep{Soarimalala2011}. Tenrecs are one of only four endemic mammalian clades in Madagascar and the small mammal species they resemble are absent from the island \citep{Garbutt1999}. Therefore, it appears that tenrecs represent an adaptive radiation of species which filled otherwise vacant ecological niches \citep{Soarimalala2011}.

	Although tenrecs are often cited as an example of both an adaptive radiation and exceptional convergent evolution \citep{Soarimalala2011, Eisenberg1969}, these claims have not been investigated quantitatively. There are qualitative similarities among the hind limb morphologies of tenrecs and several other unrelated species with similar locomotory styles \citep{Salton2009} but the degree of morphological similarity has not been established. Morphological diversity is an important feature of adaptive radiations \citep{Losos2010a} and it also informs our understanding of convergent phenotypes \citep{Muschick2012}. Therefore, it is important to quantify patterns of morphological diversity in tenrecs to gain an insight into their evolution.

@@

\section{Materials and Methods}

	Our methods involved i) data collection, ii) geometric morphometric analyses and iii) estimating morphological diversity. For clarity,  Figure \ref{fig:flow} summarises all of these steps and we describe them in detail below.

% Methods flow chart
	\begin{figure}[!htbp]
	\centering
	\includegraphics[width=1\linewidth,height=0.8\textheight]{figures/methods_flowchart_paper.png}

@@

\subsection{Data collection}
	One of us (SF) collected data from five museums: Natural History Museum, London (BMNH), Smithsonian Institute Natural History Museum, Washington D.C. (SI), American Museum of Natural History, New York (AMNH), Museum of Comparative Zoology, Cambridge M.A. (MCZ) and Field Museum of Natural History, Chicago (FMNH). We used the taxonomy in Wilson and Reeder's Mammal Species of the World \citeyearpar{Wilson2005}, except for recently identified species where we used the taxonomy recorded on the specimen labels. Wilson and Reeder \citeyearpar{Wilson2005} record 30 species of tenrec but more recent studies indicate that there are now 34 species \citep[][]{Olson2013}. The additional species belong to the shrew tenrec (\textit{Microgale}) Genus and represent either recognition of cryptic species boundaries \citep{Olson2004} or discovery of new species \citep{Goodman2006, Olson2009}. Only one of these four recent additions, \textit{M. jobihely}, was present in the museum collections and therefore we could not include the three other newly recognised species in the analyses. 
 	We photographed all of the tenrec and golden mole skulls available in the collections. This included 31 of the 34 species in the tenrec Family and 12 of the 21 species of golden moles \citep{Wilson2005}.

	We took pictures of the skulls using photographic copy stands. To take possible light variability into account, on each day we took a photograph of a white sheet of paper and used the custom white balance function on the camera to set the image as the baseline "white" measurement for those particular light conditions.

	We photographed the specimens with a Canon EOS 650D camera fitted with a EF 100 mm f/2.8 Macro USM lens. We used a remote control (H\"ahnel Combi TF) to take the photos to avoid camera shake. We photographed the specimens on a black material background with a light source in the top left-hand corner of the photograph. We used small bean bags as necessary to hold the specimens in position while being photographed to ensure that they lay in a flat plane relative to the camera. We used the grid-line function on the live-view display screen of the camera to position the specimens in the centre of each image.

	We photographed the skulls in three views: dorsal, ventral and lateral (right side) (Figure \ref{fig:flow}). When the right sides of the skulls were damaged or incomplete, we photographed the left sides and later reflected the images so that they could be compared to pictures of the right sides \citep[e.g.][]{Barrow2008}.

	We converted the raw files to binary (grey scale) images and re-saved them as TIFF files \citep[uncompressed files preserve greater detail, ][]{RHOI2013}. 
	Photographs of the specimens from the American Museum of Natural History and the Smithsonian Institute Natural History Museum are available on figshare in separate file sets for the dorsal \citep{Finlay2013d}, ventral \citep{Finlay2013v} and lateral \citep{Finlay2013l} skull views. Copyright restrictions from the other museums prevent public sharing of their images but they are available on request.

@@

@@

%Maybe move this to the supplementary?
% NC: Can it just be condensed?
	When using semilandmark approaches there is a potential problem of over-sampling: simpler structures will require fewer semilandmarks to accurately represent their shape \citep{MacLeod2012}. To ensure that we applied a uniform standard of shape representation to each outline segment (i.e. that simple structures would not be over-represented and more complex features would not be under-represented), we followed the method outlined by MacLeod \citeyearpar{MacLeod2012}. For each data set we chose a random selection of photos of specimens which represented the breadth of the morphological data (i.e. specimens from each sub-group of species). We drew the appropriate curves on each specimen and over-sampled the number of points on the curves. We measured the length of the line and regarded that as the 100\%, true length of that outline. We then re-sampled the curves with decreasing numbers of points and measured the length of the outlines. We calculated the length of each re-sampled curve as a percentage of the total length of the curve and then found the average percentage length for that reduced number of semilandmark points across all of the specimens in my test file. We continued this process until we found the minimum number of points that gave a curve length which was at least 95\% accurate.  We repeated these curve-sampling tests for each analysis to determine the minimum number of semilandmark points which would give accurate representations of morphological shape.

@@

	For each analysis, we used the \texttt{gpagen} function in the geomorph package \citep{Adams2013} to run a general Procrustes alignment \citep{Rohlf1993} of the landmark coordinates while sliding the semilandmarks by minimising Procrustes distance \citep{Bookstein1997}. We used these Procrustes-aligned coordinates of all specimens to calculate average shape values for each species which we then used for a principal components (PC) analysis with the \texttt{plotTangentSpace} function \citep{Adams2013}. We selected the number of principal component (PC) axes that accounted for 95\% of the variation in the data (Figure \ref{fig:flow}) and used these axes to estimate morphological diversity in each Family.
%-------------------------------------------------------	
\subsection{Estimating morphological diversity}

	We grouped the PC scores for tenrecs and golden moles separately so that we could estimate the diversity of each Family and then compare the two groups (Figure \ref{fig:flow}). We compared morphological diversity in two ways. First, we used non parametric multivariate analysis of variance \citep[npMANOVA;][]{Anderson2001} to test whether tenrecs and golden moles occupied significantly different positions within the morphospaces defined by the PC axes that accounted for 95\% of the overall variation in the data \citep[e.g.][]{Serb2011, Ruta2013}. A significant difference between the two Families would indicate that they have unique morphologies which do not overlap. Second, we compared morphological diversity within tenrecs to the diversity within golden moles. We define morphological diversity as the mean Euclidean distance (sum of squared differences) between each species and its Family centroid (Figure \ref{fig:centroids}). This is summarised in the equation below where \textit{n} is the number of species in the Family, \textit{i} is the number of PC axes and \textit{c} is the average PC score for each axis (the centroid).

@@

	In addition to the differences among the three skull views, our results indicate that, in skulls at least, the overall morphological diversity within tenrecs is not as large as is often assumed \citep[e.g.][]{Eisenberg1969, Olson2013}. Studies of morphological variation are sensitive to the sampling used. If a particular morphotype is over-represented then the similarities among those species will reduce the overall morphological variation within the group \citep{Foote1991}. This appears to be the case for our data; it was only when we included a sub-sample of \textit{Microgale} tenrecs that we found higher morphological diversity in tenrecs compared to golden moles across all three skull analyses (Table \ref{tab:diversity}).
	While there are clear physical differences among Family members \citep{Olson2013, Eisenberg1969}, the majority of tenrecs are very morphologically similar \citep{Jenkins2003} so morphological diversity in the Family as a whole is not as large as it first appears.  
	The goal of our study was to quantify morphological variation in tenrecs instead of relying on subjective assessments of their high morphological diversity \citep{Olson2013, Soarimalala2011, Eisenberg1969}. However, it is difficult to quantify overall morphological diversity because any study is inevitably constrained by its choice of specific traits \citep{Roy1997}. Variation in skull shape is only one aspect of overall morphology. Quantifying variation in other morphological traits could yield different patterns. Therefore future work should extend our approach beyond skulls to gain a more complete understanding of the overall morphological diversity of tenrecs and golden moles.
	%I combined the paragraph above within the discussion (previously it was part of a separate caveats section)
	While recognising these limitations, our results provide valuable insights into the differences between subjective and quantitative assessments of morphological diversity.

\section{Conclusions}
	We have presented the first quantitative investigation of morphological diversity in tenrecs. Our results indicate that, overall, tenrec skulls are not more morphologically diverse than golden moles and that similarities among the species rich \textit{Microgale} tenrecs mask signals of higher morphological diversity among the rest of the Family. Of course the results presented here are restricted to just one axis of morphological variation and further analysis of other traits is required. However, our findings provide a foundation for future investigations and represent a significant step towards a more quantitative understanding of patterns of morphological and evolutionary diversity in tenrecs.

\section{Acknowledgements}
	We thank Thomas Guillerme, Fran\c{c}ois Gould and the members of NERD club for their insightful discussions and comments. Thank you to museum staff and curators for facilitating our access to their collections: Leona Leonard and Nigel Monaghan (Natural History Museum, Ireland), Roberto Portela Miguez and Paula Jenkins (Natural History Museum, London), Esther Langan (Smithsonian Institute NMNH), Eileen Westwig (American Museum of Natural History), Judy Chupasko (Museum of Comparative Zoology) and Bill Stanley and Steve Goodman (Field Museum).

% Bibliography

\bibliographystyle{sysbio} 
\bibliography{refs_paper}
